The Astropy Project

### 2017-11-18 main.tex

The development of the \astropypkg core package began as a largely
community-driven effort to standardize core functionality for astronomical
software in \python.
In this way, its genesis differs from but builds upon many substantial and
% * <bsipocz@gmail.com> 2017-11-13T13:13:08.884Z:
%
% how do astroy builds upon these? or it's more like builds upon the developer experience?
%
%
% ^.
former astronomical software development efforts that were commissioned or
initiated through large institutional support, for example IRAF \citep[developed
at NOAO;][]{IRAF}, MIDAS \citep[developed at ESO;][]{MIDAS}, or Starlink
\citep[originally developed by a consortium of UK institutions and now
maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
% More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}
\inlinecomment{BMS}{I like the idea to reference yt here}
%
\inlinecomment{Tom R}{Python calls itself a programming language or general-purpose language, not specifically scripting language. I would remove 'scripting' below.}
\inlinecomment{Perry G}{Yes, it's time to drop the scripting adjective; it's far more general than that now.}
\python\footnote{\url{https://www.python.org/}} is an increasingly popular,
general-purpose scripting language that is available under a permissive open
source software license free of charge for all major operating systems.
Stable and well-developed packages provide support for array representation and arithmetic
\citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{numpy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}. Tens of thousands of other packages
are available which can help with tasks that are not astronomy specific but
might be performed in the course of astronomical research, for example interfacing with databases or statistical inference.

>>>>

The development of the \astropypkg core package began as a largely
community-driven effort to standardize core functionality for astronomical
software in \python.
In this way, its genesis differs from but builds upon many substantial and
% * <bsipocz@gmail.com> 2017-11-13T13:13:08.884Z:
%
% how do astroy builds upon these? or it's more like builds upon the developer experience?
%
%
% ^.
former astronomical software development efforts that were commissioned or
initiated through large institutional support, for example IRAF \citep[developed
at NOAO;][]{IRAF}, MIDAS \citep[developed at ESO;][]{MIDAS}, or Starlink
\citep[originally developed by a consortium of UK institutions and now
maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
% More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}
\inlinecomment{BMS}{I like the idea to reference yt here}
%
\python\footnote{\url{https://www.python.org/}} is an increasingly popular,
general-purpose programming language that is available under a permissive open
source software license free of charge for all major operating systems.
Stable and well-developed packages provide support for array representation and arithmetic
\citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{numpy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}. Tens of thousands of other packages
are available which can help with tasks that are not astronomy specific but
might be performed in the course of astronomical research, for example interfacing with databases or statistical inference.
